---
title: "Campsite Sweeps"
author: "Katy McKinney-Bock"
output: html_notebook
---

# Imports
```{r}
library(tidyverse)
library(readr)
library(jsonlite)
```

```{r}
# Requirements:
#     Sweeps file must have a neighborhoods column; can be created via spatialjoin.py.
SWEEPS = "../data/sweeps/sweeps_neighborhoods_joined_v04.csv"
```

Plot Functions:
```{r}
month_counts_plot <- function(data, date_col, counts_col, title, count_axis_label, fill_color="darkblue")
          {
          plot <- ggplot(data, aes(date_col, counts_col)) +
                   geom_bar(stat="identity", fill=fill_color) +
                   ggtitle(title) +
                   xlab("Date") + ylab(count_axis_label) +
                   theme(axis.text.x=element_text(size  = 10,
                                        angle = 45,
                                        hjust = 1,
                                        vjust = 1))
          return(plot)
          }
```

# Read in file, convert dates:
* Check date format
```{r}
sweeps<-read.csv(file=SWEEPS,header=TRUE)
sweeps<- cbind(sweeps, as.Date(sweeps$ReportDate, "%m/%d/%Y"))
colnames(sweeps)[colnames(sweeps)=="as.Date(sweeps$ReportDate, \"%m/%d/%Y\")"] <- "NewReportDate"
```

Aggregate by month:
```{r}
ReportDate2 <- as.Date(sweeps$NewReportDate)
short.date = strftime(ReportDate2, "%Y-%m")
sweeps.month = aggregate(Location~short.date, FUN = length, data=sweeps)
colnames(sweeps.month)<- c("Month","Count")
```

## What is average number of sweeps per week? Per month?
```{r}
m.avg<- mean(sweeps.month$Count)
m.med<- median(sweeps.month$Count)
print("By Month, average and median:") 
m.avg
m.med
```


# 3-neighborhood subset:
```{r}
sweeps.sub <- 
  sweeps %>%
  filter(NAME %in% c("HOSFORD-ABERNETHY", "BUCKMAN", "KERNS"))
```

3-neighborhood subset, aggregated:
```{r}
ReportDate2 <- as.Date(sweeps.sub$NewReportDate)
short.date = strftime(ReportDate2, "%Y-%m")
sweeps.sub.month = aggregate(Location~short.date, FUN = length, data=sweeps.sub)
colnames(sweeps.sub.month)<- c("Month","Count")
```

## What is average number of sweeps per week? Per month?
```{r}
m.avg<- mean(sweeps.sub.month$Location)
m.med<- median(sweeps.sub.month$Location)
print("By Month, Buckman/Hosford-Abernethy/Kerns,  average and median:") 
m.avg
m.med
```

# Plots
```{r}
MonthPlot <- month_counts_plot(sweeps.month, sweeps.month$Month, sweeps.month$Count, 
                               "Campsite Sweeps  \n 2016-2018", "Number of Sites Swept")
MonthPlot

MonthPlot.sub <- month_counts_plot(sweeps.sub.month, sweeps.sub.month$Month, sweeps.sub.month$Count,                                "Campsite Sweeps, Buckman/Hosford-Abernety/Kerns  \n 2016-2018", 
                                "Number of Sites Swept",
                                "purple")
MonthPlot.sub <- MonthPlot.sub +
                 scale_y_continuous(limit = c(0, 100))
MonthPlot.sub

MonthPlot.sub_samescale <- MonthPlot.sub +
                           scale_y_continuous(limit = c(0, 300))
MonthPlot.sub_samescale

ggsave(filename="MonthPlot_v04.pdf", plot=MonthPlot)
ggsave(filename="MonthPlot_3neighborhoods_v04.pdf", plot=MonthPlot.sub)
ggsave(filename="MonthPlot_3neighborhoods_samescale_v04.pdf", plot=MonthPlot.sub_samescale)
```

# Weekly Aggregate:
Aggregate by week, all PDX:
```{r}
Week = strftime(sweeps$NewReportDate, "%Y-%m-%d")
sweeps.week <-  aggregate(ReportDate~Week,FUN=length,data=sweeps)
colnames(sweeps.week)<-c("Week","Count")
```

```{r TEMP workspace for weekly sweeps}
names(sweeps.week) = c("Week", "Count")
sweeps.week %>% 
    toJSON() %>%
    write_lines("CampsiteSweeps_CountsbyWeek.json")

TEMP <- month_counts_plot(sweeps.week, sweeps.week$Week, sweeps.week$Count,
                           "Campsite Sweeps, weekly  \n 2016-2018", 
                                "Number of Sites Swept",
                                "dark blue")

TEMP

TEMP2 <- ggplot(sweeps.week, aes(x=Week, group=1)) +
          geom_line(aes(y = Count, colour="Count")) +
          theme(axis.text.x=element_text(size  = 10,
                                        angle = 45,
                                        hjust = 1,
                                        vjust = 1))

TEMP2

```


## What is average number of sweeps per week?
```{r}
m.avg<- mean(sweeps.week$Count)
m.med<- median(sweeps.week$Count)
print("By Week,  average and median:") 
m.avg
m.med

sd(sweeps.week$Count)
```

3-neighborhood subset:
```{r}
Week <- strftime(sweeps.sub$NewReportDate, "%Y-%m-%d")
sweeps.sub.week <-  aggregate(ReportDate~Week,FUN=length,data=sweeps.sub)
colnames(sweeps.sub.week)<-c("Week","Count")
```

## What is average number of sweeps per week for the subset?
```{r}
m.avg<- mean(sweeps.sub.week$Count)
m.med<- median(sweeps.sub.week$Count)
print("By Week,  average and median:") 
m.avg
m.med

print("Standard Deviation, weekly:")
sd(sweeps.sub.week$Count)
```


```{r}
WeekPlot <- month_counts_plot(sweeps.week, sweeps.week$Week, sweeps.week$Count, 
                               "Campsite Sweeps  \n 2016-2018", "Number of Sites Swept")
WeekPlot

WeekPlot.sub <- month_counts_plot(sweeps.sub.week, sweeps.sub.week$Week, sweeps.sub.week$Count,                                "Campsite Sweeps, Buckman/Hosford-Abernety/Kerns  \n 2016-2018", 
                                "Number of Sites Swept",
                                "purple")
WeekPlot.sub <- WeekPlot.sub +
                 scale_y_continuous(limit = c(0, 30))
WeekPlot.sub

WeekPlot.sub_samescale <- WeekPlot.sub +
                           scale_y_continuous(limit = c(0, 70))
WeekPlot.sub_samescale

ggsave(filename="WeekPlot.pdf", plot=WeekPlot)
ggsave(filename="WeekPlot_3neighborhoods.pdf", plot=WeekPlot.sub)
ggsave(filename="WeekPlot_3neighborhoods_samescale_.pdf", plot=WeekPlot.sub_samescale)
```


# Average for 2018 for sweeps per week:
```{r}
sweeps.week.2018 <- sweeps.week %>% filter(Week >= as.Date("2018-01-01") & Week <= as.Date("2018-10-31"))
sweeps.week.2017 <- sweeps.week %>% filter(Week >= as.Date("2017-01-01") & Week <= as.Date("2017-12-31"))

mean(sweeps.week.2018$Count)

sum(sweeps.week.2018$Count)
sum(sweeps.week.2017$Count)

```

# Write out aggregates to csv/JSON
```{r}
names(sweeps.month) = c("Month", "Count")
sweeps.month %>% 
    toJSON() %>%
    write_lines("Sweeps_CountsbyMonth.json")

names(sweeps.sub.month) = c("Month", "Count")
sweeps.sub.month %>% 
    toJSON() %>%
    write_lines("Sweeps_CountsbyMonth_3neighborhoods.json")

sweeps.sub.week %>% 
    toJSON() %>%
    write_lines("Sweeps_CountsbyWeek_3neighborhoods.json")
```

