---
title: "One Point of Contact Reports"
output: html_notebook
---

# Imports and Cleaning
```{r library}
library(tidyverse)
library(stringr)
library(readr)
library(jsonlite)
library(ggplot2)
library(ISOweek)
library(outliers)
```

```{r data}
# Requirements:
#     One Point Reports file must have a neighborhoods column to do subset; can be created via 
#     spatialjoin.py.
#
#     NOTE TO SELF: I need to re-clean and REPROJECT this dataset using the ipython notebook.
#     Can only do this once I figure out which coordinate system to project to (talk with Lynn)
#     Then, I can do the cleaning and re-estimate the number of campers. It will then go into R; maybe 
#     some changes to the import and cleaning functions may have to happen.

ONEPOINT = "../data/onepointcontactreports/campsite_reports_processed_deidentified_neighborhoods_joined_02.csv"
UNIQUE = "../data/onepointcontactreports/UniqueSites/uniquesites.csv"

```

Plot Functions:
```{r functions}
month_counts_plot <- function(data, date_col, counts_col, title, count_axis_label, fill_color="darkred")
          {
          plot <- ggplot(data, aes(date_col, counts_col)) +
                   geom_bar(stat="identity", fill=fill_color) +
                   ggtitle(title) +
                   xlab("Date") + ylab(count_axis_label) +
                   theme(axis.text.x=element_text(size  = 10,
                                        angle = 45,
                                        hjust = 1,
                                        vjust = 1))
          return(plot)
          }
```

Read in file, convert dates:
```{r read in file and date column}
reports<-read.csv(file=ONEPOINT,header=TRUE,na.strings="")

out<-str_split(reports$Date.Created, " ")
dttime<-data.frame(do.call(rbind, out), reports)
colnames(dttime)[1] <- "Date.Created.New"
colnames(dttime)[2] <- "Time.Created"
reports <- dttime
rm(dttime, out)

reports<- cbind(reports, as.Date(reports$Date.Created.New, "%m/%d/%y"))
colnames(reports)[colnames(reports)=="as.Date(reports$Date.Created.New, \"%m/%d/%y\")"] <- "NewReportDate"
```

Filter out Vehicles:
```{r vehicle filter for reports}
reports <-  
            reports %>%
               filter(!(reports[23] == TRUE))

#NEED TO KEEP THE BLANKS
write.csv(reports, file="reports_vehicle_filter_final.csv")
```


# Monthly Reports
Aggregate by month:
```{r full reports month aggregation}
ReportDate2 <- as.Date(reports$NewReportDate)
short.date = strftime(ReportDate2, "%Y-%m")
reports.month = aggregate(Date.Created.New~short.date, FUN = length, data=reports)
```

What is average number of reports per week? Per month?
```{r full reports average and median}
m.avg<- mean(reports.month$Date.Created.New)
m.med<- median(reports.month$Date.Created.New)
print("By Month, average and median:") 
m.avg
m.med
```

3-neighborhood subset:
```{r make 3neigh subset}
reports.sub <- 
  reports %>%
  filter(NAME %in% c("HOSFORD-ABERNETHY", "BUCKMAN", "KERNS"))
```

3-neighborhood subset, aggregated:
```{r 3neigh month aggregation}
ReportDate2 <- as.Date(reports.sub$NewReportDate)
short.date = strftime(ReportDate2, "%Y-%m")
reports.sub.month = aggregate(Date.Created.New~short.date, FUN = length, data=reports.sub)
```

Plots
```{r month plots full and sub}
MonthPlot <- month_counts_plot(reports.month, reports.month$short.date, reports.month$Date.Created.New, 
                               "One Point of Contact Reports  \n 2015-2018", "Number of Sites Reported")
MonthPlot

MonthPlot.sub <- month_counts_plot(reports.sub.month, reports.sub.month$short.date, 
                                   reports.sub.month$Date.Created.New,                                
                          "One Point of Contact Reports , Buckman/Hosford-Abernethy/Kerns  \n 2015-2018", 
                                   "Number of Sites Reported",
                                   "purple")
MonthPlot.sub <- MonthPlot.sub +
                 scale_y_continuous(limit = c(0, 600))
MonthPlot.sub

MonthPlot.sub_samescale <- MonthPlot.sub +
                           scale_y_continuous(limit = c(0, 4000))
MonthPlot.sub_samescale

ggsave(filename="OnePointofContact_MonthPlot.pdf", plot=MonthPlot)
ggsave(filename="OnePointofContact_MonthPlot_3neighborhoods.pdf", plot=MonthPlot.sub)
ggsave(filename="OnePointofContact_MonthPlot_3neighborhoods_samescale.pdf", plot=MonthPlot.sub_samescale)
```


# Weekly Reports:
Add date column by week:
```{r full reports daily to weekly report date conversion}
# date2ISOweek("2018-03-02")
# ISOweek2date("2018-W09-1")

WeekDateISO <-  date2ISOweek(reports$NewReportDate)
WeekDateISO <- 
                data.frame(WeekDateISO) %>%
                  rowwise() %>%
                  mutate(WeekDateISO_stripped = substring(WeekDateISO,0,8)) %>%
                  mutate(WeekDateISO_new = paste0(WeekDateISO_stripped, "-1"))
WeekDateFinal <- ISOweek2date(WeekDateISO$WeekDateISO_new)
reports <- cbind(WeekDateFinal, reports)
```

Aggregate by week:
```{r full reports weekly aggregation}
Week = strftime(reports$WeekDateFinal, "%Y-%m-%d")
reports.week <-  aggregate(Date.Created~Week,FUN=length,data=reports)
```

3-neighborhood subset, with weekdate:
```{r 3neigh sub from reports data again with weekly column}
reports.sub <- 
  reports %>%
  filter(NAME %in% c("HOSFORD-ABERNETHY", "BUCKMAN", "KERNS"))
```

3-neighborhood subset, aggregated:
```{r 3neigh weekly aggregation}
week.date = strftime(reports.sub$WeekDateFinal, "%Y-%m-%d")
reports.sub.week = aggregate(Date.Created~week.date, FUN = length, data=reports.sub)
```

Plots
```{r week plots full and 3neigh}
WeekPlot <- month_counts_plot(reports.week, reports.week$Week, reports.week$Date.Created, 
                               "One Point of Contact Reports  \n 2015-2018", "Number of Sites Reported")
WeekPlot

WeekPlot.sub <- month_counts_plot(reports.sub.week, reports.sub.week$week.date, 
                                   reports.sub.week$Date.Created,                                
                          "One Point of Contact Reports , Buckman/Hosford-Abernethy/Kerns  \n 2015-2018", 
                                   "Number of Sites Reported",
                                   "purple")
WeekPlot.sub <- WeekPlot.sub +
                 scale_y_continuous(limit = c(0, 200))
WeekPlot.sub

WeekPlot.sub_samescale <- WeekPlot.sub +
                           scale_y_continuous(limit = c(0, 800))
WeekPlot.sub_samescale

ggsave(filename="OnePointofContact_WeekPlot.pdf", plot=WeekPlot)
ggsave(filename="OnePointofContact_WeekPlot_3neighborhoods.pdf", plot=WeekPlot.sub)
ggsave(filename="OnePointofContact_WeekPlot_3neighborhoods_samescale.pdf", plot=WeekPlot.sub_samescale)
```


# Unique Sites vs Campsite Reports with Vehicles

NOTES:
Vehicles don't appear to be reported T/F until around 6/2015. Note the above restrictions on campsite reports. 

Reload reports, with vehicles:
```{r reload reports to keep vehicles and add week conversion}
reports.vehicles<-read.csv(file=ONEPOINT,header=TRUE,na.strings="")

out<-str_split(reports.vehicles$Date.Created, " ")
dttime<-data.frame(do.call(rbind, out), reports.vehicles)
colnames(dttime)[1] <- "Date.Created.New"
colnames(dttime)[2] <- "Time.Created"
reports.vehicles <- dttime
rm(dttime, out)

reports.vehicles<- cbind(reports.vehicles, as.Date(reports.vehicles$Date.Created.New, "%m/%d/%y"))
colnames(reports.vehicles)[colnames(reports.vehicles)=="as.Date(reports.vehicles$Date.Created.New, \"%m/%d/%y\")"] <- "NewReportDate"


WeekDateISO <-  date2ISOweek(reports.vehicles$NewReportDate)
WeekDateISO <- 
                data.frame(WeekDateISO) %>%
                  rowwise() %>%
                  mutate(WeekDateISO_stripped = substring(WeekDateISO,0,8)) %>%
                  mutate(WeekDateISO_new = paste0(WeekDateISO_stripped, "-1"))
WeekDateFinal <- ISOweek2date(WeekDateISO$WeekDateISO_new)
reports.vehicles <- cbind(WeekDateFinal, reports.vehicles)
```

Aggregate with vehicles, by week:
```{r reports with vehicles weekly aggregation}
Week = strftime(reports.vehicles$WeekDateFinal, "%Y-%m-%d")
reports.vehicles.week <-  aggregate(Date.Created~Week,FUN=length,data=reports.vehicles)
```

```{r write reports with vehicles and rep.veh weekly agg to json for ara}
reports.vehicles %>% 
    toJSON() %>%
    write_lines("OnePointofContact_ReportsWithVehicles_AllPDX.json")

names(reports.vehicles.week) = c("Week", "Count")
reports.vehicles.week %>% 
    toJSON() %>%
    write_lines("OnePointofContact_ReportsWithVehicles_AllPDX_weeklyaggregate.json")

write.csv(reports.vehicles.week, "OnePointofContact_ReportsWithVehicles_AllPDX_weeklyaggregate.csv")
```


```{r read estimated unique campsites and add counts with vehicles column}
unique <- read.csv(UNIQUE)
Week <- as.Date(unique$Date, "%m/%d/%y")
unique <- cbind(Week, unique)

reports.vehicles.week$Week <- as.Date(reports.vehicles.week$Week)

all_counts1 <- left_join(unique, reports.vehicles.week, by="Week")
colnames(all_counts1) <- c("Week", "Date" , "TotalReports_CityCount", "EstimatedSites",  "Count_AllReports")

reports.week$Week <- as.Date(reports.week$Week)
all_counts <- left_join(all_counts1, reports.week, by="Week")
colnames(all_counts) <- c("Week", "Date" , "TotalReports_CityCount", "EstimatedSites",  "Count_AllReports", "Count_NoVehicles")
```

```{r plot with campsite reports with and wo vehicles and unique sites}

alllines <- ggplot(all_counts, aes(x=Week)) +
              geom_line(aes(y = EstimatedSites, colour = "EstimatedSites")) + 
              geom_point(aes(y = EstimatedSites, colour = "EstimatedSites")) + 
              geom_line(aes(y = Count_AllReports, colour = "Count_AllReports")) +
              geom_point(aes(y = Count_AllReports, colour = "Count_AllReports")) + 
              geom_line(aes(y = Count_NoVehicles, colour = "Count_NoVehicles")) +
              geom_point(aes(y = Count_NoVehicles, colour = "Count_NoVehicles"))

alllines


ggsave(filename="OnePointofContact_3Lines.pdf", plot=alllines)
```

Make a plot of the unique campsites reported each week, alone.
```{r plot with unique est sites alone weekly plus average}
mean(all_counts$EstimatedSites)
sd(all_counts$EstimatedSites)
  
estsites <- ggplot(all_counts, aes(x=Week)) +
              geom_line(aes(y = EstimatedSites, colour = "EstimatedSites")) + 
              geom_point(aes(y = EstimatedSites, colour = "EstimatedSites")) +
              ylim(0, 200)

estsites

ggsave(filename="OnePointofContact_EstimatedSites.pdf", plot=estsites)
```

Make a plot of the count of campsites (without vehicles) reported each week PER unique campsite reported.
NOTE: This is _on average_, as one campsite may have gotten 30 reports, and another just 1.
```{r }
all_counts <-
        all_counts %>%
        mutate(Reports_per_UniqueSite = Count_NoVehicles / EstimatedSites)

plot <- ggplot(all_counts, aes(Week)) +
        geom_line(aes(y = Reports_per_UniqueSite, colour = "Reports_per_UniqueSite")) + 
        ylim(0,6)
ggsave(filename="OnePointofContact_Reports_per_UniqueSite_Estimated.pdf", plot=plot)
```


# Bar plot with the total counts (as well as averages per week) of reports for 2015, 2016, 2017, 2018

Aggregate by Year, no Vehicles
```{r all reports no vehicles yearly aggregate}
ReportDate2 <- as.Date(reports$NewReportDate)
Year = strftime(ReportDate2, "%Y")
reports.annual = aggregate(Date.Created.New~Year, FUN = length, data=reports)
```

Aggregate by Year, with Vehicles
```{r all reports WITH vehicles yearly aggregate}
ReportDate2 <- as.Date(reports.vehicles$NewReportDate)
Year = strftime(ReportDate2, "%Y")
reports.vehicles.annual = aggregate(Date.Created.New~Year, FUN = length, data=reports.vehicles)
```

Bar Plot, annual counts (with Vehicles)
```{r annual bar plot with vehicles}
reports.vehicles.annual2 <-
    reports.vehicles.annual %>%
    filter(!(Year=="2015"))

annualplot <- month_counts_plot(reports.vehicles.annual2, reports.vehicles.annual2$Year, reports.vehicles.annual2$Date.Created.New, 
                               "One Point of Contact Reports  \n 2016-2018", "Total Counts", "dark orange")

annualplot

ggsave(filename="OnePointofContact_Reports_AnnualTotal.pdf", plot=annualplot)
```

Bar Plot, Average Reports per week for the year.

3-neighborhood subset:
```{r make 3neigh subset for reports with vehicles}
reports.vehicles.sub <- 
  reports.vehicles %>%
  filter(NAME %in% c("HOSFORD-ABERNETHY", "BUCKMAN", "KERNS"))
```
Aggregate by Year, with Vehicles
```{r 3neigh sub yearly aggregate all reports with vehicles}
ReportDate2 <- as.Date(reports.vehicles.sub$NewReportDate)
Year = strftime(ReportDate2, "%Y")
reports.vehicles.sub.annual = aggregate(Date.Created.New~Year, FUN = length, data=reports.vehicles.sub)
```

Bar Plot, annual counts (with Vehicles)
```{r bar plot 3neigh annual}
reports.vehicles.sub.annual2 <-
    reports.vehicles.sub.annual %>%
    filter(!(Year=="2015"))

annualplot.sub <- month_counts_plot(reports.vehicles.sub.annual2, reports.vehicles.sub.annual2$Year, reports.vehicles.sub.annual2$Date.Created.New, 
                               "One Point of Contact Reports  \n 2016-2018", "Hosford-Abernethy, Buckman, Kerns", "dark orange")

annualplot.sub

ggsave(filename="OnePointofContact_Reports_AnnualTotal_3neighborhoods.pdf", plot=annualplot.sub)
```


# Ratio of sweeps to reports, 2018:
```{r}
all_counts$Week
all_counts$Count_AllReports

all_counts.2018 <- all_counts %>%
                    filter(Week >= as.Date("2018-01-01") & Week <="2018-11-25")

sum(all_counts.2018$Count_AllReports) / sum(all_counts.2018$EstimatedSites)

```

# Write out aggregates to JSON
```{r write all files to JSON}
names(reports.month) = c("Month", "Count")
reports.month %>% 
    toJSON() %>%
    write_lines("OnePointofContact_CountsbyMonth.json")

names(reports.week) = c("Week", "Count")
reports.week %>% 
    toJSON() %>%
    write_lines("OnePointofContact_CountsbyWeek.json")

names(reports.sub.month) = c("Month", "Count")
reports.sub.month %>% 
    toJSON() %>%
    write_lines("OnePointofContact_CountsbyMonth_3neighborhood.json")

names(reports.sub.week) = c("Week", "Count")
reports.sub.week %>% 
    toJSON() %>%
    write_lines("OnePointofContact_CountsbyWeek_3neighborhood.json")

all_counts %>% 
    toJSON() %>%
    write_lines("OnePointofContact_AllCounts_AllPDX.json")

```

# Next Step: Analysis of qualitative information, 'problematic' criteria.

Improve Header Names
```{r change header names for reports with vehicles}
colnames(reports.vehicles)
betternames<-c("WeekDate", "Date.Created.New", "Time.Created", "IDX", 
               "Date.Created", "Date.Received", 
               "ItemID","Status","Follow-ups", "Location1","Location2","Location3",
               "Address.ID", "Property.ID", "State.ID", "City", 
               "HowLongSite","Occupied",
               "NumCampers_str",        
               "Children","Dogs","MedicalFragility","NumTentsStructures","Vehicle","Aggression",
               "IntoxDrugs",
               "ObstructsRightofWay","MisusePublicSpaces","StructuresTentsPresent","ExcessiveTrash",
               "DamageEnvironment","lon","lat","coordinates", "index_right", "NAME", "SUM_AREA",
               "SUM_SqMile", "NewReportDate")

colnames(reports.vehicles)<-betternames
```

Exploration of survey fields/responses of Full Data over ALL time, location
```{r reports.vehicles survey responses aggregated}
#Is the site occupied?
occ<-aggregate(IDX~Occupied,FUN=length,data=reports.vehicles)
occ

#Children present
children<-aggregate(IDX~Children,FUN=length,data=reports.vehicles)
children

#Dogs present
dogs<-aggregate(IDX~Dogs,FUN=length,data=reports.vehicles)
dogs

#Medically Fragile people
med<-aggregate(IDX~MedicalFragility,FUN=length,data=reports.vehicles)
med
```

Distribution of the "Problem" fields/questions on the survey for the full dataset
```{r problem field analysis aggression}
#Aggressive Behavior
P01<-aggregate(IDX~Aggression,FUN=length,data=reports.vehicles)
P01

P01$fraction = P01$IDX / sum(P01$IDX)
P01$ymax = cumsum(P01$fraction)
P01$ymin = c(0, head(P01$ymax, n=-1))

Aggression <- ggplot(P01, aes(fill=Aggression, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Aggressive Behavior")

Aggression

ggsave(Aggression, file="Aggresion.png")
```


```{r problem field analysis intoxication drugs}
#Intoxication or Drugs
P02<-aggregate(IDX~IntoxDrugs,FUN=length,data=reports.vehicles)
P02

P02$fraction = P02$IDX / sum(P02$IDX)
P02$ymax = cumsum(P02$fraction)
P02$ymin = c(0, head(P02$ymax, n=-1))

Intoxication <- ggplot(P02, aes(fill=IntoxDrugs, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Intoxication and/or Drugs")

Intoxication

ggsave(Intoxication, file="Intoxication.png")
```


```{r problem field analysis public right of way}
#Obstructs Public Right-of-Way
P03<-aggregate(IDX~ObstructsRightofWay,FUN=length,data=reports.vehicles)
P03

P03$fraction = P03$IDX / sum(P03$IDX)
P03$ymax = cumsum(P03$fraction)
P03$ymin = c(0, head(P03$ymax, n=-1))

RightofWay <- ggplot(P03, aes(fill=ObstructsRightofWay, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Obstructs Public Right-of-Way")

RightofWay

ggsave(RightofWay, file="RightofWay.png")
```

```{r problem field analysis public spaces}
#Misuse of Public Spaces
P04<-aggregate(IDX~MisusePublicSpaces,FUN=length,data=reports.vehicles)
P04


P04$fraction = P04$IDX / sum(P04$IDX)
P04$ymax = cumsum(P04$fraction)
P04$ymin = c(0, head(P04$ymax, n=-1))

MisuseofPublicSpaces <- ggplot(P04, aes(fill=MisusePublicSpaces, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Misuse of Public Spaces")

MisuseofPublicSpaces

ggsave(MisuseofPublicSpaces, file="MisuseofPublicSpaces.png")
```

```{r problem field analysis structures or tents}
#Are structures or tents present?
P05<-aggregate(IDX~StructuresTentsPresent,FUN=length,data=reports.vehicles)
P05

P05$fraction = P05$IDX / sum(P05$IDX)
P05$ymax = cumsum(P05$fraction)
P05$ymin = c(0, head(P05$ymax, n=-1))

Tents <- ggplot(P05, aes(fill=StructuresTentsPresent, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Are Structures or Tents Present")

Tents

ggsave(Tents, file="Tents.png")
```

```{r problem field analysis trash biohazard}
#Excessive trash or biohazards
P06<-aggregate(IDX~ExcessiveTrash,FUN=length,data=reports.vehicles)
P06
P06 <- P06[-2,]

P06$fraction = P06$IDX / sum(P06$IDX)
P06$ymax = cumsum(P06$fraction)
P06$ymin = c(0, head(P06$ymax, n=-1))

Biohazard <- ggplot(P06, aes(fill=ExcessiveTrash, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Excessive Trash or Biohazard")

Biohazard

ggsave(Biohazard, file="Biohazard.png")

```

```{r problem field analysis damage to environment}
#Damage to the environment
P07<-aggregate(IDX~DamageEnvironment,FUN=length,data=reports.vehicles)
P07<- P07[-2,]

P07$fraction = P07$IDX / sum(P07$IDX)
P07$ymax = cumsum(P07$fraction)
P07$ymin = c(0, head(P07$ymax, n=-1))


EnvironmentDamage <- ggplot(P07, aes(fill=DamageEnvironment, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Damage to the Environment")

EnvironmentDamage

ggsave(EnvironmentDamage, file="EnvironmentDamage.png")
```


How many have children? Dogs? Medically fragile people?
```{r reports.vehicles children dogs medical}
#Is the site occupied?
occ2<-aggregate(IDX~Occupied,FUN=length,data=reports.vehicles)
occ2

#need to replace no/No/not sure/yes/8-Jun. 
#quick subset for Sandra

occ_temp <- occ[-1,]
occ_temp <- occ_temp[-2,]

occ_temp

occ_temp$fraction = occ_temp$IDX / sum(occ_temp$IDX)
occ_temp$ymax = cumsum(occ_temp$fraction)
occ_temp$ymin = c(0, head(occ_temp$ymax, n=-1))

occupied <- ggplot(occ_temp, aes(fill=Occupied, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Is the Site Occupied")

occupied
```

```{r}
#Children present
children2<-aggregate(IDX~Children,FUN=length,data=reports.vehicles)
children2

children2$fraction = children2$IDX / sum(children2$IDX)
children2$ymax = cumsum(children2$fraction)
children2$ymin = c(0, head(children2$ymax, n=-1))

childrenplot <- ggplot(children2, aes(fill=Children, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Are Children Present?")

childrenplot
```

```{r}
#Dogs present
dogs2<-aggregate(IDX~Dogs,FUN=length,data=reports.vehicles)
dogs2

dogs2$fraction = dogs2$IDX / sum(dogs2$IDX)
dogs2$ymax = cumsum(dogs2$fraction)
dogs2$ymin = c(0, head(dogs2$ymax, n=-1))

dogsplot <- ggplot(dogs2, aes(fill=Dogs, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Are Dogs Present?")

dogsplot
```

```{r}
#Medically Fragile people
med2<-aggregate(IDX~MedicalFragility,FUN=length,data=reports.vehicles)
med2

med2 <- med2[-1,]
med2
falsies <- med2[1,2] + med2[2,2]
truesies <- med2[3,2] + med2[4,2]


IDX<- c(truesies, falsies)
MedicalFragility <- c("TRUE", "FALSE")
med2<-data.frame(MedicalFragility, IDX)


med2$fraction = med2$IDX / sum(med2$IDX)
med2$ymax = cumsum(med2$fraction)
med2$ymin = c(0, head(med2$ymax, n=-1))

med2plot <- ggplot(med2, aes(fill=MedicalFragility, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Are Medically Fragile People Present?")

med2plot
```

```{r write donut files to JSON}

P07 %>% 
    toJSON() %>%
    write_lines("EnvironmentDamage.json")

P06 %>% 
    toJSON() %>%
    write_lines("BiohazardTrash.json")

P05 %>% 
    toJSON() %>%
    write_lines("TentsPresent.json")

P04 %>% 
    toJSON() %>%
    write_lines("MisusePublicSpaces.json")

P03 %>% 
    toJSON() %>%
    write_lines("ObstructsRightofWay.json")

P02 %>% 
    toJSON() %>%
    write_lines("IntoxDrugs.json")

P01 %>% 
    toJSON() %>%
    write_lines("Aggression.json")
```


### Estimating the number of campers
Reimport the dataset (with the num_campers column:)
```{r}
REIMPORT = "Replicate_Num_campers_correction/campsite_reports_with_num_campers_spatial_join.csv"
numcamps = read.csv(REIMPORT)
```

Average number of people reported per campsite (descriptive statistics):
```{r}
summary(numcamps$number_of_campers)

numcamps$number_of_campers
max(numcamps$number_of_campers, na.rm=TRUE)

numcamps$number_of_campers[which(numcamps$number_of_campers == max(numcamps$number_of_campers, na.rm=TRUE))]
which(numcamps$number_of_campers == max(numcamps$number_of_campers, na.rm=TRUE))

numcamps[17173,]
sub2 <- numcamps[-17173,]

summary(sub2$number_of_campers)
which(sub2$number_of_campers== max(sub2$number_of_campers, na.rm=TRUE))
sub2[30839,]

sub3<-sub2[-30839,]


summary(sub3$number_of_campers)
which(sub3$number_of_campers== max(sub3$number_of_campers, na.rm=TRUE))
sub3[31337,]

sub4<-sub3[-31337,]
summary(sub4$number_of_campers)
which(sub4$number_of_campers== max(sub4$number_of_campers, na.rm=TRUE))
sub4[22196,]

```

Outlier removal before mean:
```{r}
outlier(numcamps$number_of_campers)

boxplot(numcamps$number_of_campers)
mine<-boxplot(numcamps$number_of_campers)
outliers<-mine$out
mine$names
mine$stats

min(outliers)
max(outliers)
sub.noout<-numcamps[numcamps$number_of_campers<12.5,]

boxplot(sub.noout$number_of_campers)
summary(sub.noout$number_of_campers)
```

Average number of campers per site: 4.065 (if assume trim of <50, then it's 5; if assume heavy trim of 12.5, then it's 3.6).
